Think deep for reef resilience

### 2025-08-17 paper/paper_draft.qmd
Update prediction performance plots and insert section into results

### Partial dependence

@@

@@

>>>>

#### Partial dependence

@@

Assessing random forest prediction performance reveals increasing performance as bioregion
mean reef depth and carrying capacity increase [@sfig-rf-predictor-perf]. This highlights
where there is unexplained variation between reefs that contributes to cluster assignment
and reef cover outcomes but is not captured by our included predictor variables.

@@

![Scatter plots indicating the bioregion test-prediction accuracy (proportion of reefs in
each bioregion assigned correct clusters) from the Random Forest model. Plot panels
represent the bioregion accuracy across various predictor ranges and bioregion attributes,
such as mean bioregion depth, carrying capacity, DHW value, total connectivity strength,
Source-to-sink ratio and the number of reefs in each
bioregion.](../figs/rf_performance_across_predictors.png){#sfig-rf-predictor-perf
fig-align="center" width="14.82cm"}
